\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting with black underlines
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands for listing
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Yogesh Kumar Singh} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 8303906144 ~ 
    \href{mailto:yogesh75232000@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{yogesh75232000@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/yogesh-kumar-singh-b61406224/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
    \href{https://github.com/Yogesh-7523}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
    \href{https://leetcode.com/your_leetcode_username}{\raisebox{-0.2\height}\faBook\ \underline{LeetCode}}
    \vspace{-8pt}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\begin{itemize}[leftmargin=*,label={}]
\item
Software Engineer with 1 years designing scalable Java and Spring Boot microservices, experienced with REST APIs, JWT auth, Docker, Redis, CI/CD, and system design. Proven record increasing reliability and reducing transaction failures significantly.
\end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\small
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt, parsep=0pt, topsep=0pt]
    \item \textbf{Languages}: Java, Python, SQL
    \item \textbf{Frameworks}: Spring Boot, Spring Security, Spring Cloud, Feign, Resilience4j
    \item \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis
    \item \textbf{Cloud}: AWS EC2, S3, AppConfig
    \item \textbf{DevOps/Tools}: Git, Docker, Jenkins, Maven, Postman, JUnit, SonarQube, Fortify
    \item \textbf{Concepts}: Microservices, REST APIs, JWT Authentication, Caching, CI/CD, SOLID, Agile, System Design, Linux
\end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Systems Engineer, Tata Consultancy Services}{Feb 2025 -- Present}
    {Noida, Uttar Pradesh, India}{}
\resumeItemListStart
    \resumeItem{Designed and deployed 20+ RESTful APIs for GeM 2.0 (Government e-Marketplace) using Spring Boot and PostgreSQL, improving response times by 30\% and supporting 10k+ daily users.}
    \resumeItem{Built and maintained a scalable microservices architecture with Spring Cloud, improving service reliability and reducing release cycle time by 25\%.}
    \resumeItem{Implemented automated CI/CD pipelines using Jenkins for seamless build, test, and deployment across multiple environments.}
    \resumeItem{Integrated AWS S3 for secure and efficient file storage and retrieval, streamlining document management workflows and reducing server load by 25\%.}
    \resumeItem{Resolved Fortify and SonarQube issues by addressing critical and major vulnerabilities, ensuring compliance with secure coding and code quality standards.}
    \resumeItem{Deployed and configured microservices on AWS EC2, managing environment properties using AWS AppConfig.}
    \resumeItem{Orchestrated the creation and execution of over 100 JUnit and Mockito unit/integration tests, achieving 85\% code coverage and cutting development defects by 40\%, accelerating release cycles.}
    \resumeItem{Refactored legacy modules adhering to OOP principles, Controller–Facade-Service–Repository patterns, and SOLID design principles, reducing technical debt by 20\%.}
    \resumeItem{Optimized API performance through Redis caching, efficient query design, and asynchronous message processing using Apache Kafka.}
    \resumeItem{Collaborated with cross-functional teams using Agile/Scrum methodology, contributing to sprint planning, code reviews, and continuous integration improvements.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
    {PredictFlow - Smart Payment Retry Engine}{Oct 2024 -- Present}
    {}{}
    \resumeItemListStart
        \resumeItem{Engineered payment retry system with 3 Spring Boot microservices, reducing failed retries by 60\%.}
        \resumeItem{Implemented JWT authentication with Redis token blacklist and role-based access control for security.}
        \resumeItem{Developed rule-based retry prediction using error type, time, and retry count to prevent retry storms.}
        \resumeItem{Utilized Redis caching and Resilience4j circuit breaker patterns to ensure high availability.}
        \resumeItem{Containerized with Docker Compose for streamlined deployment and scalability.}
        \resumeItem{Achieved 85\%+ test coverage with JUnit, enabling reliable production releases.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
    {KIET Group of Institutions}{Nov 2020 -- Jun 2024}
    {Bachelor of Technology in Computer Science and Engineering}{CGPA: 8.0/10}
    \resumeItemListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, itemsep=0pt, parsep=0pt, topsep=0pt]
    \item Open-Source Contributor, GSSOC 2023
    \item Global Nominee and Regional Winner, NASA Space Apps Challenge 2022
    \item Runner-up, THacks 2.0 Hackathon
    \item Contributor to Hacktoberfest, 2021 & 2022
\end{itemize}

\end{document}
